### 2012-12-02 report/paper.tex
Initial paper build system
Signed-off-by: Sam Phippen <samphippen@googlemail.com>

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

\documentclass{acm_proc_article-sp}

\begin{document}

\title{A Sample {\ttlit ACM} SIG Proceedings Paper in LaTeX
Format\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
\subtitle{[Extended Abstract]
\titlenote{A full version of this paper is available as
\textit{Author's Guide to Preparing ACM SIG Proceedings Using
\LaTeX$2_\epsilon$\ and BibTeX} at
\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Wallamaloo, New Zealand}\\
       \email{trovato@corporation.com}
% 2nd. author
\alignauthor
G.K.M. Tobin\titlenote{The secretary disavows
any knowledge of this author's actions.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
% 3rd. author
\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
one who did all the really hard work.}\\
       \affaddr{The Th{\o}rv{\"a}ld Group}\\
       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
       \affaddr{Hekla, Iceland}\\
       \email{larst@affiliation.org}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Lawrence P. Leipuner\\
       \affaddr{Brookhaven Laboratories}\\
       \affaddr{Brookhaven National Lab}\\
       \affaddr{P.O. Box 5000}\\
       \email{lleipuner@researchlabs.org}
% 5th. author
\alignauthor Sean Fogarty\\
       \affaddr{NASA Ames Research Center}\\
       \affaddr{Moffett Field}\\
       \affaddr{California 94035}\\
       \email{fogartys@amesres.org}
% 6th. author
\alignauthor Charles Palmer\\
       \affaddr{Palmer Research Laboratories}\\
       \affaddr{8600 Datapoint Drive}\\
       \affaddr{San Antonio, Texas 78229}\\
       \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms to
the formatting guidelines for ACM SIG Proceedings.
It complements the document \textit{Author's Guide to Preparing
ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file.
\end{abstract}

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Theory}

\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings

\section{Introduction}
The \textit{proceedings} are the records of a conference.
ACM seeks to give these conference by-products a uniform,
high-quality appearance.  To do this, ACM has some rigid
requirements for the format of the proceedings documents: there
is a specified format (balanced  double columns), a specified
set of fonts (Arial or Helvetica and Times Roman) in
certain specified sizes (for instance, 9 point for body copy),
a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
and (1.9 cm [.75"]) left and right; specified column width
(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).

The good news is, with only a handful of manual
settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
and {\texttt{\char'134 alignauthor}} commands, you have
already used; another, {\texttt{\char'134 balancecolumns}}, will
be used in your very last run of \LaTeX\ to ensure
balanced column heights on the last page.}, the \LaTeX\ document
class file handles all of this for you.

The remainder of this document is concerned with showing, in
the context of an ``actual'' document, the \LaTeX\ commands
specifically available for denoting the structure of a
proceedings paper, rather than with giving rigorous descriptions
or explanations of such commands.

\section{The {\secit Body} of The Paper}
Typically, the body of a paper is organized
into a hierarchical structure, with numbered or unnumbered
headings for sections, subsections, sub-subsections, and even
smaller sections.  The command \texttt{{\char'134}section} that
precedes this paragraph is part of such a
hierarchy.\footnote{This is the second footnote.  It
starts a series of three footnotes that add nothing
informational, but just give an idea of how footnotes work
and look. It is a wordy one, just so you see
how a longish one plays out.} \LaTeX\ handles the numbering
and placement of these headings for you, when you use
the appropriate heading commands around the titles
of the headings.  If you want a sub-subsection or
smaller part to be unnumbered in your output, simply append an
asterisk to the command name.  Examples of both
numbered and unnumbered headings will appear throughout the
balance of this sample document.

Because the entire article is contained in
the \textbf{document} environment, you can indicate the
start of a new paragraph with a blank line in your
input file; that is why this sentence forms a separate paragraph.

\subsection{Type Changes and {\subsecit Special} Characters}
We have already seen several typeface changes in this sample.  You
can indicate italicized words or phrases in your text with
the command \texttt{{\char'134}textit}; emboldening with the
command \texttt{{\char'134}textbf}
and typewriter-style (for instance, for computer code) with
\texttt{{\char'134}texttt}.  But remember, you do not
have to indicate typestyle changes when such changes are
part of the \textit{structural} elements of your
article; for instance, the heading of this subsection will
be in a sans serif\footnote{A third footnote, here.
Let's make this a rather short one to
see how it looks.} typeface, but that is handled by the
document class file. Take care with the use
of\footnote{A fourth, and last, footnote.}
the curly braces in typeface changes; they mark
the beginning and end of
the text that is to be in the different typeface.

You can use whatever symbols, accented characters, or
non-English characters you need anywhere in your document;
you can find a complete list of what is
available in the \textit{\LaTeX\
User's Guide}\cite{Lamport:LaTeX}.

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\subsubsection{Inline (In-text) Equations}
A formula that appears in the running text is called an
inline or in-text formula.  It is produced by the
\textbf{math} environment, which can be
invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
construction or with the short form \texttt{\$. . .\$}. You
can use any of the symbols and structures,
from $\alpha$ to $\omega$, available in
\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
few examples of in-text equations in context. Notice how
this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsubsection{Display Equations}
A numbered display equation -- one set off by vertical space
from the text and centered horizontally -- is produced
by the \textbf{equation} environment. An unnumbered display
equation is produced by the \textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols
and structures available in \LaTeX; this section will just
give a couple of examples of display equations in context.
First, consider the equation, shown as an inline equation above:
\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
and follow it with another numbered equation:
\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\subsection{Citations}
Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
conference
proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
in the Bibliography section of your
article will occur throughout the text of your article.
You should use BibTeX to automatically produce this bibliography;
you simply need to insert one of several citation commands with
a key of the item cited in the proper location in
the \texttt{.tex} file \cite{Lamport:LaTeX}.
The key is a short reference you invent to uniquely
identify each work; in this sample document, the key is
the first author's surname and a
word from the title.  This identifying key is included
with each item in the \texttt{.bib} file for your article.

The details of the construction of the \texttt{.bib} file
are beyond the scope of this sample document, but more
information can be found in the \textit{Author's Guide},
and exhaustive details in the \textit{\LaTeX\ User's
Guide}\cite{Lamport:LaTeX}.

This article shows only the plainest form
of the citation command, using \texttt{{\char'134}cite}.
This is what is stipulated in the SIGS style specifications.
No other citation format is endorsed.

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
is found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table 1 is included in the input file; compare the
placement of the table here with the table in the printed
dvi output of this document.

\begin{table}
\centering
\caption{Frequency of Special Characters}
\begin{tabular}{|c|c|l|} \hline
Non-English or Math&Frequency&Comments\\ \hline
\O & 1 in 1,000& For Swedish names\\ \hline
$\pi$ & 1 in 5& Common in math\\ \hline
\$ & 4 in 5 & Used in business\\ \hline
$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
\hline\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of
the page's live area, use the environment
\textbf{table*} to enclose the table's contents and
the table caption.  As with a single-column table, this wide
table will ``float" to a location deemed more desirable.
Immediately following this sentence is the point at which
Table 2 is included in the input file; again, it is
instructive to compare the placement of the
table here with the table in the printed dvi
output of this document.

\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\subsection{Figures}
Like tables, figures cannot be split across pages; the
best placement for them
is typically the top or the bottom of the page nearest
their initial cite.  To ensure this proper ``floating'' placement
of figures, use the environment
\textbf{figure} to enclose the figure and its caption.

This sample document contains examples of \textbf{.eps}
and \textbf{.ps} files to be displayable with \LaTeX.  More
details on each of these is found in the \textit{Author's Guide}.

As was the case with tables, you may want a figure
that spans two columns.  To do this, and still to
ensure proper ``floating'' placement of tables, use the environment
\textbf{figure*} to enclose the figure and its caption.

Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
used; use
the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
commands as appropriate for the different file types.

\subsection{Theorem-like Constructs}
Other common constructs that may occur in your article are
the forms for logical constructs like theorems, axioms,
corollaries and proofs.  There are
two forms, one produced by the
command \texttt{{\char'134}newtheorem} and the
other by the command \texttt{{\char'134}newdef}; perhaps
the clearest and easiest way to distinguish them is
to compare the two in the output of this sample document:

This uses the \textbf{theorem} environment, created by
the\linebreak\texttt{{\char'134}newtheorem} command:
\newtheorem{theorem}{Theorem}
\begin{theorem}
Let $f$ be continuous on $[a,b]$.  If $G$ is
an antiderivative for $f$ on $[a,b]$, then
\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
\end{theorem}

The other uses the \textbf{definition} environment, created
by the \texttt{{\char'134}newdef} command:
\newdef{definition}{Definition}
\begin{definition}
If $z$ is irrational, then by $e^z$ we mean the
unique number which has
logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
\end{definition}

Two lists of constructs that use one of these
forms is given in the
\textit{Author's  Guidelines}.

and don't forget to end the environment with
{figure*}, not {figure}!

There is one other similar construct environment, which is
already set up
for you; i.e. you must \textit{not} use
a \texttt{{\char'134}newdef} command to
create it: the \textbf{proof} environment.  Here
is a example of its use:
\begin{proof}
Suppose on the contrary there exists a real number $L$ such that
\begin{displaymath}
\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
\end{displaymath}
Then
\begin{displaymath}
l=\lim_{x\rightarrow c} f(x)
= \lim_{x\rightarrow c}
\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
\frac{f(x)}{g(x)} = 0\cdot L = 0,
\end{displaymath}
which contradicts our assumption that $l\neq 0$.
\end{proof}

Complete rules about using these environments and using the
two different creation commands are in the
\textit{Author's Guide}; please consult it for more
detailed instructions.  If you need to use another construct,
not listed therein, which you want to have the same
formatting as the Theorem
or the Definition\cite{salas:calculus} shown above,
use the \texttt{{\char'134}newtheorem} or the
\texttt{{\char'134}newdef} command,
respectively, to create it.

\subsection*{A {\secit Caveat} for the \TeX\ Expert}
Because you have just been given permission to
use the \texttt{{\char'134}newdef} command to create a
new form, you might think you can
use \TeX's \texttt{{\char'134}def} to create a
new command: \textit{Please refrain from doing this!}
Remember that your \LaTeX\ source code is primarily intended
to create camera-ready copy, but may be converted
to other forms -- e.g. HTML. If you inadvertently omit
some or all of the \texttt{{\char'134}def}s recompilation will
be, to say the least, problematic.

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for
the body of the article are different in the appendices.
In the \textbf{appendix} environment, the command
\textbf{section} is used to
indicate the start of each Appendix, with alphabetic order
designation (i.e. the first is A, the second B, etc.) and
a title (if you include one).  So, if you need
hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this
document in Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{Acknowledgments}
\subsection{Additional Authors}
This section is inserted by \LaTeX; you do not insert it.
You just add the names and information in the
\texttt{{\char'134}additionalauthors} command at the start
of the document.
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}
The acm\_proc\_article-sp document class file itself is chock-full of succinct
and helpful comments.  If you consider yourself a moderately
experienced to expert user of \LaTeX, you may find reading
it useful but please remember not to change it.
\balancecolumns
% That's all folks!
\end{document}

### 2012-12-02 BSE.py
Added graphing for buyer and seller bids/asks, limits and equilibriums.

@@ -48,7 +48,6 @@
 import sys
 import random
 import aa_trader
-import aa_agent
 
 bse_sys_minprice = 1    # minimum price in the system, in cents/pennies
 bse_sys_maxprice = 1000 # maximum price in the system, in cents/pennies
@@ -758,8 +757,6 @@ def populate_market(traders_spec, traders, shuffle, verbose):
                         return Trader_ZIP('ZIP', name, 0.00)
                 elif robottype == 'AA':
                         return aa_trader.AATrader('AA', name, 0.00)
-                elif robottype == 'AA2':
-                        return aa_agent.AAAgent('AA2', name, 0.00)
                 else:
                         sys.exit('FATAL: don\'t know robot type %s\n' % robottype)
 
@@ -1052,7 +1049,9 @@ def market_session(sess_id, starttime, endtime, trader_spec, order_schedule, dum
         # write trade_stats for this experiment NB end-of-session summary only
         trade_stats(sess_id, traders, tdump, time, exchange.publish_lob(time, lob_verbose))
 
-
+        for t in traders:
+            if traders[t].ttype == "AA":
+                traders[t].graph_values()
 
 #############################
 
@@ -1077,7 +1076,7 @@ if __name__ == "__main__":
         order_sched = {'sup':supply_schedule, 'dem':demand_schedule,
                        'interval':30, 'timemode':'drip-poisson'}
 
-        buyers_spec = [('ZIC',10),('AA2',1)]
+        buyers_spec = [('ZIC',10),('AA',1)]
         sellers_spec = buyers_spec
         traders_spec = {'sellers':sellers_spec, 'buyers':buyers_spec}
 

### 2012-12-02 aa_core.py

@@ -3,8 +3,7 @@ import BSE
 import copy
 
 import math
-import random
-
+import matplotlib.pyplot as plt
 
 #guesswork comment!
 ALPHA_MIN = 0.02;
@@ -69,6 +68,8 @@ class AACommon:
 
         # DEBUG
         self.strval = ""
+        self.bids = []
+        self.asks = []
 
     def interesting_trades(self):
         return self.previous_trades
@@ -145,7 +146,29 @@ class AACommon:
         #print "aa eq", mean
         print "aa eq", self.equilibrium_price
         self.equilibrium_price = mean
-
+        
+    def graph_values(self):
+        data = None
+        mode = None
+        if len(self.bids) > 0:
+            mode = "buy"
+            data = self.bids
+        elif len(self.asks) > 0:
+            mode = "sell"
+            data = self.asks
+        if mode != None:
+            times = [x["time"] for x in data]
+            prices = [x["price"] for x in data]
+            limits = [x["limit"] for x in data]
+            equs = [x["equ"] for x in data]
+            if mode == "buy":
+                plt.figure(1)
+                plt.plot(times, prices, 'ro', times, limits, 'rx', times, equs, 'r-')
+            else:
+                plt.figure(2)
+                plt.plot(times, prices, 'bo', times, limits, 'bx', times, equs, 'b-')
+            plt.savefig("figures/" + mode + "_image.png")
+        
 class AABuyer(AACommon):
 
     def __init__(self):
@@ -235,6 +258,7 @@ class AABuyer(AACommon):
             else:
                 print "aab bc case d"
                 bid = market_best_bid + (self.tau-market_best_bid)/self.nyan
+            self.bids.append({"tid":order.tid, "price":bid, "time":time, "limit":order.price, "equ":self.equilibrium_price})
             return BSE.Order(order.tid, "Bid", bid, order.qty, time)
         return None
 
@@ -327,5 +351,6 @@ class AASeller(AACommon):
                 print "aas bc case d"
                 ask = market_best_ask - (market_best_ask - self.tau)/self.nyan
                 assert ask >= self.limit_price()
+            self.asks.append({"tid":order.tid, "price":ask, "time":time, "limit":order.price, "equ":self.equilibrium_price})
             return BSE.Order(order.tid, "Ask", ask, order.qty, time)
         return None

### 2012-12-02 aa_trader.py

@@ -83,6 +83,7 @@ class AATrader(BSE.Trader):
         o = self.buyer_agent.bidding_component(best_ask_price, best_bid_price, time)
         if o is not None:
             print "aa making a trade"
+            print "graph", "BID", o.price, o.time
             if o.price < BSE.bse_sys_minprice:
                 print "aa price", o.price
                 print "aa clamping"
@@ -102,6 +103,7 @@ class AATrader(BSE.Trader):
         o = self.seller_agent.bidding_component(best_ask_price, best_bid_price, time)
         if o is not None:
             print "aa making a trade"
+            print "graph", "ASK", o.price, o.time
             if o.price > BSE.bse_sys_maxprice:
                 o.price = BSE.bse_sys_maxprice
             print "aas o", o
@@ -116,3 +118,7 @@ class AATrader(BSE.Trader):
         if trade is not None:
             self.buyer_agent.receive_trade(trade)
             self.seller_agent.receive_trade(trade)
+            
+    def graph_values(self):
+        self.buyer_agent.graph_values()
+        self.seller_agent.graph_values()

### 2012-12-02 BSE.py
updates for luke's graphing Signed-off-by: Lukeus Maximus <lm9131@bristol.ac.uk>

@@ -48,6 +48,7 @@
 import sys
 import random
 import aa_trader
+import matplotlib.pyplot as plt
 
 bse_sys_minprice = 1    # minimum price in the system, in cents/pennies
 bse_sys_maxprice = 1000 # maximum price in the system, in cents/pennies
@@ -1002,6 +1003,8 @@ def market_session(sess_id, starttime, endtime, trader_spec, order_schedule, dum
 
         pending_orders = []       
 
+        orders_returned = []
+
         while time < endtime:
 
                 # how much time left, as a percentage?
@@ -1021,6 +1024,7 @@ def market_session(sess_id, starttime, endtime, trader_spec, order_schedule, dum
                 print "dat trader", tid
 
                 if order != None:
+                        orders_returned.append((traders[tid].ttype, order))
                         # send order to exchange
                         trade = exchange.process_order2(time, order, True)
                         if trade != None:
@@ -1039,6 +1043,7 @@ def market_session(sess_id, starttime, endtime, trader_spec, order_schedule, dum
                                 traders[t].respond(time, lob, trade, respond_verbose)
 
                         print "aa lob", lob
+                        
                 time = time + timestep
 
 
@@ -1049,11 +1054,46 @@ def market_session(sess_id, starttime, endtime, trader_spec, order_schedule, dum
         # write trade_stats for this experiment NB end-of-session summary only
         trade_stats(sess_id, traders, tdump, time, exchange.publish_lob(time, lob_verbose))
 
+        make_pretty_graph(orders_returned, traders_spec["buyers"], endtime)
+
         for t in traders:
             if traders[t].ttype == "AA":
-                traders[t].graph_values()
+                traders[t].graph_values(traders_spec["buyers"], endtime)
 
 #############################
+
+def make_pretty_graph(orders_returned, spec, length):
+    types = []
+    for o in orders_returned:
+        if not (o[0] in types):
+            types.append(o[0])
+    bids = [x for x in orders_returned if x[1].otype == "Bid"]
+    asks = [x for x in orders_returned if x[1].otype == "Ask"]
+    spec_str = ""
+    for x in spec:
+        spec_str += x[0] + str(x[1])
+    for t in types:
+        type_orders = [x[1] for x in bids if x[0] == t]
+        times = [x.time for x in type_orders]
[…]

### 2012-12-02 aa_core.py

@@ -42,6 +42,9 @@ class RoundRobinBuffer:
     def __iter__(self):
         return self.buffer.__iter__()
 
+plotted_buy = False
+plotted_sell = False
+
 class AACommon:
     def __init__(self):
         #-1 is most aggressive
@@ -147,13 +150,14 @@ class AACommon:
         print "aa eq", self.equilibrium_price
         self.equilibrium_price = mean
         
-    def graph_values(self):
+    def graph_values(self, spec, length):
+        global plotted_buy, plotted_sell
         data = None
         mode = None
-        if len(self.bids) > 0:
+        if not plotted_buy and len(self.bids) > 0:
             mode = "buy"
             data = self.bids
-        elif len(self.asks) > 0:
+        elif not plotted_sell and len(self.asks) > 0:
             mode = "sell"
             data = self.asks
         if mode != None:
@@ -162,12 +166,17 @@ class AACommon:
             limits = [x["limit"] for x in data]
             equs = [x["equ"] for x in data]
             if mode == "buy":
+                plotted_buy = True
                 plt.figure(1)
                 plt.plot(times, prices, 'ro', times, limits, 'rx', times, equs, 'r-')
             else:
+                plotted_sell = True
                 plt.figure(2)
                 plt.plot(times, prices, 'bo', times, limits, 'bx', times, equs, 'b-')
-            plt.savefig("figures/" + mode + "_image.png")
+            spec_str = ""
+            for x in spec:
+                spec_str += x[0] + str(x[1])
+            plt.savefig("figures/" + spec_str + "_" + length + "_" + mode + "_image.png")
         
 class AABuyer(AACommon):
 

### 2012-12-02 aa_trader.py

@@ -119,6 +119,6 @@ class AATrader(BSE.Trader):
             self.buyer_agent.receive_trade(trade)
             self.seller_agent.receive_trade(trade)
             
-    def graph_values(self):
-        self.buyer_agent.graph_values()
-        self.seller_agent.graph_values()
+    def graph_values(self, spec):
+        self.buyer_agent.graph_values(spec)
+        self.seller_agent.graph_values(spec)

### 2012-12-02 report/paper.tex
More report
Signed-off-by: Sam Phippen <samphippen@googlemail.com>

@@
-% THIS IS SIGPROC-SP.TEX - VERSION 3.1
-% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
-% APRIL 2009
-%
-% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
-% LaTeX2e document class file for Conference Proceedings submissions.
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) Page numbering
-% ---------------------------------------------------------------------------------------------------------------
-% It is an example which *does* use the .bib file (from which the .bbl file
-% is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission,
-% you need to 'insert'  your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% Questions regarding SIGS should be sent to
-% Adrienne Griscti ---> griscti@acm.org
-%
-% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
-% Gerald Murray ---> murray@hq.acm.org
-%
-% For tracking purposes - this is V3.1SP - APRIL 2009
-
 \documentclass{acm_proc_article-sp}
@@
 
-\title{A Sample {\ttlit ACM} SIG Proceedings Paper in LaTeX
-Format\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
-\subtitle{[Extended Abstract]
-\titlenote{A full version of this paper is available as
-\textit{Author's Guide to Preparing ACM SIG Proceedings Using
-\LaTeX$2_\epsilon$\ and BibTeX} at
-\texttt{www.acm.org/eaddress.htm}}}
+\title{Algorithmic and Economic Aspects of the Internet}
 %
@@
 
-\numberofauthors{8} %  in this sample file, there are a *total*
+\numberofauthors{2} %  in this sample file, there are a *total*
 % of EIGHT authors. SIX appear on the 'first-page' (for formatting
@@
 \alignauthor
-Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{1932 Wallamaloo Lane}\\
-       \affaddr{Wallamaloo, New Zealand}\\
-       \email{trovato@corporation.com}
+Sam Phippen\titlenote{sp9857}\\
+       \email{samphippen@googlemail.com}
 % 2nd. author
 \alignauthor
-G.K.M. Tobin\titlenote{The secretary disavows
-any knowledge of this author's actions.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{P.O. Box 1212}\\
-       \affaddr{Dublin, Ohio 43017-6221}\\
-       \email{webmaster@marysville-ohio.com}
-% 3rd. author
-\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
-one who did all the really hard work.}\\
-       \affaddr{The Th{\o}rv{\"a}ld Group}\\
-       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
-       \affaddr{Hekla, Iceland}\\
-       \email{larst@affiliation.org}
-\and  % use '\and' if you need 'another row' of author names
-% 4th. author
-\alignauthor Lawrence P. Leipuner\\
-       \affaddr{Brookhaven Laboratories}\\
-       \affaddr{Brookhaven National Lab}\\
-       \affaddr{P.O. Box 5000}\\
-       \email{lleipuner@researchlabs.org}
-% 5th. author
-\alignauthor Sean Fogarty\\
-       \affaddr{NASA Ames Research Center}\\
-       \affaddr{Moffett Field}\\
-       \affaddr{California 94035}\\
-       \email{fogartys@amesres.org}
-% 6th. author
-\alignauthor Charles Palmer\\
-       \affaddr{Palmer Research Laboratories}\\
-       \affaddr{8600 Datapoint Drive}\\
-       \affaddr{San Antonio, Texas 78229}\\
-       \email{cpalmer@prl.com}
+Luke Murray\titlenote{lm9131}
+       \email{lm9131@bris.ac.uk}
 }
@@
 % in the \additional authors block, viz.
-\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
-email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
-(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
-\date{30 July 1999}
 % Just remember to make sure that the TOTAL number of authors
@@
 \begin{abstract}
-This paper provides a sample of a \LaTeX\ document which conforms to
-the formatting guidelines for ACM SIG Proceedings.
-It complements the document \textit{Author's Guide to Preparing
-ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
-source file has been written with the intention of being
-compiled under \LaTeX$2_\epsilon$\ and BibTeX.
 
-The developers have tried to include every imaginable sort
-of ``bells and whistles", such as a subtitle, footnotes on
-title, subtitle and authors, as well as in the text, and
-every optional component (e.g. Acknowledgments, Additional
-Authors, Appendices), not to mention examples of
-equations, theorems, tables and figures.
+For the assignment we attempted to implement the Adaptive
+Aggressive\cite{Vytellingum:AA} trading agent strategy. Even with corrections
+emailed by D. Cliff we found that our strategy does not trade as efficiently as
+is implied in other background research\cite{DC:dominate}. In this paper we've
+done a comparative analysis of the existing trading agents provided in BSE,
+along with our implementation. We have also performed a post mortem analysis as
+to why we believe that our trader is not trading as efficiently as expected.
 
-To make best use of this sample document, run it through \LaTeX\
-and BibTeX, and compare this source code with the printed
-output produced by the dvi file.
+We had initially set our sights on taking an implementation of AA and trying to
+improve upon it, with a view to building something new and potentially more
+effective, however, having found ourselves in a position where the agent is
+nowhere near as effective as we expected, this was not a good springboard for
+extension.
+
 \end{abstract}
 
-% A category with the (minimum) three required fields
-\category{H.4}{Information Systems Applications}{Miscellaneous}
-%A category including the fourth, optional field follows...
-\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
+\section{Analysis of our agent with existing traders}
 
-\terms{Theory}
+\subsection {Many versus many tests} For the analysis we started with a many
+versus many test of our implementation versus each of the agents provided with
+BSE. In this experiment we used the stepped supply and demand schedule provided
+with an early version of the Bristol Stock Exchange, with three distinct time
+periods, the first having prices in the range 10-190, the second in the range
+200-300 and the third having prices in the same range as the first. In the many
+versus many test 20 agents of each type were used (10 sellers and 10 buyers),
+and the tests with this supply and demand schedule were repeated a total of 25
+times.
 
-\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings
+The table below shows the number of rounds that our agent lost, the mean
+difference in profit between the other agent and ours, and the standard
+deviation of the difference in profit also.
 
-\section{Introduction}
-The \textit{proceedings} are the records of a conference.
-ACM seeks to give these conference by-products a uniform,
-high-quality appearance.  To do this, ACM has some rigid
-requirements for the format of the proceedings documents: there
-is a specified format (balanced  double columns), a specified
-set of fonts (Arial or Helvetica and Times Roman) in
-certain specified sizes (for instance, 9 point for body copy),
-a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
-the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
-and (1.9 cm [.75"]) left and right; specified column width
-(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).
+\begin{center}
+  \begin{tabular}{ l | l | l | l }
+        Agent Type & Tests lost & $\Delta$ Profit Mean & $\Delta$ Profit StDev \\\hline
+        Giveaway & 24 & 63.84 & 34.16\\
+        ZIC & 25 & 75.38 & 36.15\\
+        Shaver & 25 & 95.63 & 21.01\\
+        Sniper & 25 & 22.67 & 12.78\\
+        ZIP & 25 & 97.08 & 41.38\\
+  \end{tabular}
+\end{center}
 
-The good news is, with only a handful of manual
-settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
-and {\texttt{\char'134 alignauthor}} commands, you have
-already used; another, {\texttt{\char'134 balancecolumns}}, will
-be used in your very last run of \LaTeX\ to ensure
-balanced column heights on the last page.}, the \LaTeX\ document
-class file handles all of this for you.
+In almost all of these cases our agent consistently generated a profit,
+however when run against the Shaver agent, an oddity occurred. The agent on
+average generated a loss which can be seen on the box plot in figure 1.
 
-The remainder of this document is concerned with showing, in
-the context of an ``actual'' document, the \LaTeX\ commands
-specifically available for denoting the structure of a
-proceedings paper, rather than with giving rigorous descriptions
-or explanations of such commands.
+\begin{figure}[h!] 
+\includegraphics[width=80mm]{box-plot-image.png}
 
-\section{The {\secit Body} of The Paper}
-Typically, the body of a paper is organized
-into a hierarchical structure, with numbered or unnumbered
-headings for sections, subsections, sub-subsections, and even
-smaller sections.  The command \texttt{{\char'134}section} that
-precedes this paragraph is part of such a
-hierarchy.\footnote{This is the second footnote.  It
-starts a series of three footnotes that add nothing
-informational, but just give an idea of how footnotes work
-and look. It is a wordy one, just so you see
-how a longish one plays out.} \LaTeX\ handles the numbering
-and placement of these headings for you, when you use
-the appropriate heading commands around the titles
-of the headings.  If you want a sub-subsection or
-smaller part to be unnumbered in your output, simply append an
-asterisk to the command name.  Examples of both
-numbered and unnumbered headings will appear throughout the
-balance of this sample document.
+\caption{Box plot of average profits of the 20 AA agents implemented by us in
+the many vs many test against shaver agents. Box plot generated from:
+http://www.alcula.com/calculators/statistics/box-plot/}
+\end{figure}
 
-Because the entire article is contained in
-the \textbf{document} environment, you can indicate the
-start of a new paragraph with a blank line in your
-input file; that is why this sentence forms a separate paragraph.
+-- insert explanation about that here.
 
-\subsection{Type Changes and {\subsecit Special} Characters}
-We have already seen several typeface changes in this sample.  You
-can indicate italicized words or phrases in your text with
-the command \texttt{{\char'134}textit}; emboldening with the
-command \texttt{{\char'134}textbf}
-and typewriter-style (for instance, for computer code) with
-\texttt{{\char'134}texttt}.  But remember, you do not
-have to indicate typestyle changes when such changes are
-part of the \textit{structural} elements of your
-article; for instance, the heading of this subsection will
-be in a sans serif\footnote{A third footnote, here.
-Let's make this a rather short one to
-see how it looks.} typeface, but that is handled by the
-document class file. Take care with the use
-of\footnote{A fourth, and last, footnote.}
-the curly braces in typeface changes; they mark
-the beginning and end of
-the text that is to be in the different typeface.
+\subsection{1 v 1 tests}
+Given these initially dismal results, we decided that a good place to start a
+detailed analysis would be a 1v1 test with the Giveaway trader, which is
+clearly the worst of all the traders within the BSE system. 300 1v1 tests were
+performed, we used the same schedule as the many versus many test. Results
+where both bots made zero profit were eliminated, this brought the number of
+tests included for analysis down from 300 to 242. Of these tests 103 were won
+by Giveaway and 139 were won by our agent. The distributions of profit for each
+agent, as well as the distribution of differences in profit can be seen in the
+following histograms.
+
+\begin{figure}[h!] \includegraphics[width=80mm]{giveaway_1_v_1.png}
+\caption{Histogram of profit distributions over 300 similar trading runs for
+the two bot types used in the 1v1 test. Note axis are different for the two
+bots} \end{figure}
+
+\begin{figure}[h!] \includegraphics[width=80mm]{giveaway_1_v_1_delta.png}
+\caption {Histogram showing the difference between Giveaway and our AA implementation,
+positive profit represents cases where Giveaway made more profit than AA}
+\end{figure}
+
+\newpage
+Upon initially inspecting these graphs we had assumed that our agent should
+lose to Giveaway, however we checked the medians of the distributions and noted
+that the median profit of the Giveaway agent (1.7) was less than the median
+profit (50.0) of our agent. We feel that this difference in profits is the
+reason for our agent's overall victory against Giveaway. To determine if the
+difference in medians is significant we decided to use the Wilcoxon signed-rank
+test\cite{wiki:wilcoxon}. We like this test because:
+
+\begin{enumerate}
+\item It makes no assumptions about the underlying
+distribution of profit pairs, as we can see from the histogram, these are
+nowhere near normally distributed.
+
+\item It handles the fact that the pairs are dependant but the individual runs
+are independent.
+
+\item We feel that the assumptions the distribution makes are fulfilled here:
+the pairs do come from the same distributions. The pairs have been generated
+largely at random by running different tests and collecting results. The data
+are obviously ordinal as they are floating amounts of profit.
+
+\end{enumerate}
+
+In order to conduct this test we represented each run as a pair of
+$(profit_{giveaway}, profit_{agent})$. The profits in the pair are taken from
+the average profit column in the output of running BSE, so in fact the profit
+values are divided by two, because their are two of each agent running in the
+system. This will not effect the output of the test, as the change in magnitude
+is the same for both agents. The test runs over the difference between the
+first and second value in the pair. Our null hypothesis $H0$ is that the median
+difference of each pair is zero, with our positive hypothesis $H1$ being that
+the median difference of each pair is not zero. We performed the test using
+scipy's built in Wilcoxon signed-rank test implementation\cite{scipy:wilcoxon}
+and the results were extremely conclusive.  With $p=1.2\times10^{-6}$ we reject
+$H0$ and conclude that the difference in medians is significant, as such the
+profits generated by our agent are significantly better than Giveaway's.
+
+This test was repeated for each of ZIC, Shaver, Sniper and ZIP. In each case
+the results were that our bot performed significantly worse than the other agent (p < 0.01
+in each case).
+
+\subsection{One in many tests}
+We also evaluated the agent initially in a one versus many test against a ZIC
+trader which gave better results. Using a similar strategy above we started
+with 25 tests to determine winners and average profits, however the results
+were not totally conclusive, so we decided to generate some 300 experimental
+results in order to attempt to draw conclusions about whether the bot performs
+better in one v many tests. The results are shown below, using the same supply
+and demand schedule, and two of our agent (1 buyer, 1 seller) and 20 of
+the other agent (10 buyers, 10 sellers):
+
+\begin{center}
+\begin{tabular}{ l|l|l|l }
+Agent Type & Tests lost & $\Delta$ Profit Mean & $\Delta$ Profit StDev \\
+\hline
+Giveaway & 157 & -2.28 & 86.95\\ 
+ZIC & 225 & 52.86 & 83.99\\ 
+Shaver & 287 & 76.36 & 46.06\\ 
+Sniper & 256 & 19.49 & 16.74\\ 
+ZIP & 234 & 64.76 & 89.76
+\end{tabular}
+\end{center}
+
+We can see here that the agent performs better when trading on it's own than in
+a small swarm.
 

### 2012-12-03 report/paper.tex
El report
Signed-off-by: Sam Phippen <samphippen@googlemail.com>

@@
 
-\subsection{1 v 1 tests}
-Given these initially dismal results, we decided that a good place to start a
-detailed analysis would be a 1v1 test with the Giveaway trader, which is
-clearly the worst of all the traders within the BSE system. 300 1v1 tests were
-performed, we used the same schedule as the many versus many test. Results
-where both bots made zero profit were eliminated, this brought the number of
-tests included for analysis down from 300 to 242. Of these tests 103 were won
-by Giveaway and 139 were won by our agent. The distributions of profit for each
-agent, as well as the distribution of differences in profit can be seen in the
-following histograms.
+\subsection{1 v 1 tests} Given these initially dismal results, we decided that
+a good place to start a detailed analysis would be a 1v1 test with the Giveaway
+trader, which is clearly the worst of all the traders within the BSE system.
+300 1v1 tests were performed, we used the same schedule as the many versus many
+test, with a longer total trading time of 1800. Results where both bots made
+zero profit were eliminated, this brought the number of tests included for
+analysis down from 300 to 242. Of these tests 103 were won by Giveaway and 139
+were won by our agent. The distributions of profit for each agent, as well as
+the distribution of differences in profit can be seen in figures 2 and 3.
 
@@
 $(profit_{giveaway}, profit_{agent})$. The profits in the pair are taken from
-the average profit column in the output of running BSE, so in fact the profit
-values are divided by two, because their are two of each agent running in the
-system. This will not effect the output of the test, as the change in magnitude
-is the same for both agents. The test runs over the difference between the
-first and second value in the pair. Our null hypothesis $H0$ is that the median
-difference of each pair is zero, with our positive hypothesis $H1$ being that
-the median difference of each pair is not zero. We performed the test using
-scipy's built in Wilcoxon signed-rank test implementation\cite{scipy:wilcoxon}
-and the results were extremely conclusive.  With $p=1.2\times10^{-6}$ we reject
-$H0$ and conclude that the difference in medians is significant, as such the
-profits generated by our agent are significantly better than Giveaway's.
+the average profit column in the output of running BSE. This means that in
+reality the profit values are divided through by two for each agent, as it is
+the average of 1 seller and 1 buyer in each case. This does not affect the test
+because the change in magnitude is the same for both agents.
 
-This test was repeated for each of ZIC, Shaver, Sniper and ZIP. In each case
-the results were that our bot performed significantly worse than the other agent (p < 0.01
-in each case).
+The test runs over the difference between the first and second value in the
+pair. Our null hypothesis $H0$ is that the median difference of each pair is
+zero, with our positive hypothesis $H1$ being that the median difference of
+each pair is not zero. We performed the test using scipy's built in Wilcoxon
+signed-rank test implementation\cite{scipy:wilcoxon} and the results were
+conclusive.  With $p=1.2\times10^{-6}$ we reject $H0$ and conclude
+that the difference in medians is significant, as such the difference in
+profits generated is statistically significant.
 
-\subsection{One in many tests}
-We also evaluated the agent initially in a one versus many test against a ZIC
-trader which gave better results. Using a similar strategy above we started
-with 25 tests to determine winners and average profits, however the results
-were not totally conclusive, so we decided to generate some 300 experimental
-results in order to attempt to draw conclusions about whether the bot performs
-better in one v many tests. The results are shown below, using the same supply
-and demand schedule, and two of our agent (1 buyer, 1 seller) and 20 of
-the other agent (10 buyers, 10 sellers):
+This test was repeated for each of ZIC, Shaver, Sniper and ZIP. In each case,
+the results were that, our agent performed worse than the other
+agent with our agent having a lower median score and the Wilcoxon test giving
+p < 0.01 in each case.
 
-\begin{center}
-\begin{tabular}{ l|l|l|l }
-Agent Type & Tests lost & $\Delta$ Profit Mean & $\Delta$ Profit StDev \\
-\hline
-Giveaway & 157 & -2.28 & 86.95\\ 
-ZIC & 225 & 52.86 & 83.99\\ 
-Shaver & 287 & 76.36 & 46.06\\ 
-Sniper & 256 & 19.49 & 16.74\\ 
-ZIP & 234 & 64.76 & 89.76
-\end{tabular}
-\end{center}
+In light of the test against Giveaway it is  worth noting the spike at a profit
+of around ~4000 in figure 3.  These occasions correspond to Giveaway making
+4000 more profit than our agent. A quick analysis of the data indicates that
+nearly all of these occur when our agent issues no trades (zero balance at the
+end of trading). As such we concluded that for whatever reason on these events
+(96/242 runs) the conditions never reach the point where our agent starts
+trading. This is not unreasonable given the warmup period of the algorithm and
+the low number of traders in the system.
 
-We can see here that the agent performs better when trading on it's own than in
-a small swarm.
+\subsection{Experiments with supply and demand schedules}
 
-You can use whatever symbols, accented characters, or
-non-English characters you need anywhere in your document;
-you can find a complete list of what is
-available in the \textit{\LaTeX\
-User's Guide}\cite{Lamport:LaTeX}.
+We wanted to determine under what, if any, supply and demand conditions our
+agent could outperform some of the better algorithms in the system. In order to
+do this we conducted several experiments with varying supply and demand
+schedules listed below. We use n=300 as our number of trials, 1 v 1 tests and a
+total time period length of 1800. Initially all tests were performed against
+ZIC
 
-\subsection{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of
-the three are discussed in the next sections.
+\subsection{Totally open market}
 
-\subsubsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an
-inline or in-text formula.  It is produced by the
-\textbf{math} environment, which can be
-invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
-construction or with the short form \texttt{\$. . .\$}. You
-can use any of the symbols and structures,
-from $\alpha$ to $\omega$, available in
-\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
-few examples of in-text equations in context. Notice how
-this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsubsection{Display Equations}
-A numbered display equation -- one set off by vertical space
-from the text and centered horizontally -- is produced
-by the \textbf{equation} environment. An unnumbered display
-equation is produced by the \textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols
-and structures available in \LaTeX; this section will just
-give a couple of examples of display equations in context.
-First, consider the equation, shown as an inline equation above:
-\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\subsection{Citations}
-Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
-conference
-proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
-in the Bibliography section of your
-article will occur throughout the text of your article.
-You should use BibTeX to automatically produce this bibliography;
-you simply need to insert one of several citation commands with
-a key of the item cited in the proper location in
-the \texttt{.tex} file \cite{Lamport:LaTeX}.
-The key is a short reference you invent to uniquely
-identify each work; in this sample document, the key is
-the first author's surname and a
-word from the title.  This identifying key is included
-with each item in the \texttt{.bib} file for your article.
-
-The details of the construction of the \texttt{.bib} file
-are beyond the scope of this sample document, but more
-information can be found in the \textit{Author's Guide},
-and exhaustive details in the \textit{\LaTeX\ User's
-Guide}\cite{Lamport:LaTeX}.
-
-This article shows only the plainest form
-of the citation command, using \texttt{{\char'134}cite}.
-This is what is stipulated in the SIGS style specifications.
-No other citation format is endorsed.
-
-\subsection{Tables}
-Because tables cannot be split across pages, the best
-placement for them is typically the top of the page
-nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and
-the table caption.  The contents of the table itself must go
-in the \textbf{tabular} environment, to
-be aligned properly in rows and columns, with the desired
-horizontal and vertical rules.  Again, detailed instructions
-on \textbf{tabular} material
-is found in the \textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table 1 is included in the input file; compare the
-placement of the table here with the table in the printed
-dvi output of this document.
-
-\begin{table}
-\centering
-\caption{Frequency of Special Characters}
-\begin{tabular}{|c|c|l|} \hline
-Non-English or Math&Frequency&Comments\\ \hline
-\O & 1 in 1,000& For Swedish names\\ \hline
-$\pi$ & 1 in 5& Common in math\\ \hline
-\$ & 4 in 5 & Used in business\\ \hline
-$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-\hline\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of
-the page's live area, use the environment
-\textbf{table*} to enclose the table's contents and
-the table caption.  As with a single-column table, this wide
-table will ``float" to a location deemed more desirable.
-Immediately following this sentence is the point at which
-Table 2 is included in the input file; again, it is
-instructive to compare the placement of the
-table here with the table in the printed dvi
-output of this document.
-
-\begin{table*}
-\centering
-\caption{Some Typical Commands}
-\begin{tabular}{|c|c|l|} \hline
-Command&A Number&Comments\\ \hline
-\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
-\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
-\texttt{{\char'134}table}& 300 & For tables\\ \hline
-\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
-\end{table*}
-% end the environment with {table*}, NOTE not {table}!
-
-\subsection{Figures}
-Like tables, figures cannot be split across pages; the
-best placement for them
-is typically the top or the bottom of the page nearest
-their initial cite.  To ensure this proper ``floating'' placement
-of figures, use the environment
-\textbf{figure} to enclose the figure and its caption.
-
-This sample document contains examples of \textbf{.eps}
-and \textbf{.ps} files to be displayable with \LaTeX.  More
-details on each of these is found in the \textit{Author's Guide}.
-
-As was the case with tables, you may want a figure
-that spans two columns.  To do this, and still to
-ensure proper ``floating'' placement of tables, use the environment
-\textbf{figure*} to enclose the figure and its caption.
-
-Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
-used; use
-the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
-commands as appropriate for the different file types.
-
-\subsection{Theorem-like Constructs}
-Other common constructs that may occur in your article are
-the forms for logical constructs like theorems, axioms,
-corollaries and proofs.  There are
-two forms, one produced by the
-command \texttt{{\char'134}newtheorem} and the
-other by the command \texttt{{\char'134}newdef}; perhaps
-the clearest and easiest way to distinguish them is
-to compare the two in the output of this sample document:
-
-This uses the \textbf{theorem} environment, created by
-the\linebreak\texttt{{\char'134}newtheorem} command:
-\newtheorem{theorem}{Theorem}
-\begin{theorem}
-Let $f$ be continuous on $[a,b]$.  If $G$ is
-an antiderivative for $f$ on $[a,b]$, then
-\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
-\end{theorem}
-
-The other uses the \textbf{definition} environment, created
-by the \texttt{{\char'134}newdef} command:
-\newdef{definition}{Definition}
-\begin{definition}
-If $z$ is irrational, then by $e^z$ we mean the
-unique number which has
-logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
-\end{definition}
-
-Two lists of constructs that use one of these
-forms is given in the
-\textit{Author's  Guidelines}.
-
-and don't forget to end the environment with
-{figure*}, not {figure}!
-
-There is one other similar construct environment, which is
-already set up
-for you; i.e. you must \textit{not} use
-a \texttt{{\char'134}newdef} command to
-create it: the \textbf{proof} environment.  Here
-is a example of its use:
-\begin{proof}
-Suppose on the contrary there exists a real number $L$ such that
-\begin{displaymath}
-\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
-\end{displaymath}
-Then
-\begin{displaymath}
-l=\lim_{x\rightarrow c} f(x)
-= \lim_{x\rightarrow c}
-\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
-= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
-\frac{f(x)}{g(x)} = 0\cdot L = 0,
-\end{displaymath}
-which contradicts our assumption that $l\neq 0$.
-\end{proof}
-
-Complete rules about using these environments and using the
-two different creation commands are in the
-\textit{Author's Guide}; please consult it for more
-detailed instructions.  If you need to use another construct,
-not listed therein, which you want to have the same
-formatting as the Theorem
-or the Definition\cite{salas:calculus} shown above,
-use the \texttt{{\char'134}newtheorem} or the
-\texttt{{\char'134}newdef} command,
-respectively, to create it.
-
-\subsection*{A {\secit Caveat} for the \TeX\ Expert}
-Because you have just been given permission to
-use the \texttt{{\char'134}newdef} command to create a
-new form, you might think you can
-use \TeX's \texttt{{\char'134}def} to create a
-new command: \textit{Please refrain from doing this!}
-Remember that your \LaTeX\ source code is primarily intended
-to create camera-ready copy, but may be converted
-to other forms -- e.g. HTML. If you inadvertently omit
-some or all of the \texttt{{\char'134}def}s recompilation will
-be, to say the least, problematic.
-
-\section{Conclusions}
-This paragraph will end the body of this sample document.
-Remember that you might still have Acknowledgments or
-Appendices; brief samples of these
-follow.  There is still the Bibliography to deal with; and
-we will make a disclaimer about that here: with the exception
-of the reference to the \LaTeX\ book, the citations in
-this paper are to articles which have nothing to
-do with the present subject and are used as
-examples only.
-%\end{document}  % This is where a 'short' article might terminate
-
-%ACKNOWLEDGMENTS are optional
-\section{Acknowledgments}
-This section is optional; it is a location for you
-to acknowledge grants, funding, editing assistance and
-what have you.  In the present case, for example, the
-authors would like to thank Gerald Murray of ACM for
-his help in codifying this \textit{Author's Guide}
-and the \textbf{.cls} and \textbf{.tex} files that it describes.
+In this set of trials we used the hard limits of BSE, minimum price of 1 and
+maximum price of 1000 for both the supply and demand curves, for the entire
+time range, using a drip-poisson timemode with a 30 second replenishment time.
+The idea behind this experiment is to gather an understanding as to how our
+agent performs in a totally unconstrained environment.
 
@@
 \appendix
-%Appendix A
-\section{Headings in Appendices}
-The rules about hierarchical headings discussed above for
-the body of the article are different in the appendices.
-In the \textbf{appendix} environment, the command
-\textbf{section} is used to
-indicate the start of each Appendix, with alphabetic order
-designation (i.e. the first is A, the second B, etc.) and
-a title (if you include one).  So, if you need
-hierarchical structure
-\textit{within} an Appendix, start with \textbf{subsection} as the
-highest level. Here is an outline of the body of this
-document in Appendix-appropriate form:
-\subsection{Introduction}
-\subsection{The Body of the Paper}
-\subsubsection{Type Changes and  Special Characters}
-\subsubsection{Math Equations}
-\paragraph{Inline (In-text) Equations}
-\paragraph{Display Equations}
-\subsubsection{Citations}
-\subsubsection{Tables}
-\subsubsection{Figures}
-\subsubsection{Theorem-like Constructs}
-\subsubsection*{A Caveat for the \TeX\ Expert}
-\subsection{Conclusions}
-\subsection{Acknowledgments}
-\subsection{Additional Authors}
-This section is inserted by \LaTeX; you do not insert it.
-You just add the names and information in the
-\texttt{{\char'134}additionalauthors} command at the start
-of the document.
-\subsection{References}
-Generated by bibtex from your ~.bib file.  Run latex,
-then bibtex, then latex twice (to resolve references)
-to create the ~.bbl file.  Insert that ~.bbl file into
-the .tex source file and comment out
-the command \texttt{{\char'134}thebibliography}.
-% This next section command marks the start of
-% Appendix B, and does not continue the present hierarchy
-\section{More Help for the Hardy}
-The acm\_proc\_article-sp document class file itself is chock-full of succinct
-and helpful comments.  If you consider yourself a moderately
-experienced to expert user of \LaTeX, you may find reading
-it useful but please remember not to change it.
-\balancecolumns
-% That's all folks!
 \end{document}

### 2012-12-03 report/paper.tex
Made more words.

@@
 
--- insert explanation about that here.
+\subsection{AA v Shaver} One very noticable trend in our analysis is when AA
+is pitched against the Shaver algorithm. In all of our experiments where trades
+occurred, Shaver made more profit than AA. In this section, we explore the
+reasons why Shaver so completely outclasses our implemetation of AA.
+
+Shaver is designed to make "close shave" bids and asks by slightly out-bidding
+the best bid on the market. This is similar to how AA's aggressiveness is
+supposed to operate; when a bid is placed that out-bids the bot, the price is
+adjusted so that the bot out-bids the previous bid in the following round
+(unless such a bid would exceed the bot's limit price). This aggressiveness
+behaviour increases the chance of a trade and thus increases profit.
+
+We show 3 cases here:
+\begin{enumerate}
+\item 1 AA bot v. 1 Shaver bot
+\item 1 AA bot v. 10 Shaver bots
+\item 10 AA bots v. 10 Shaver bots
+\end{enumerate}
+
+\subsubsection{1 v 1} No trading occurs in this experiment. In the graphs
+below, you can see the shouts made by the bots. The Shaver buyer and seller
+traders tend toward the equilibrium price over time but don't manage to reach
+it before the market session ends. The AA bot makes very few trades and is
+always out-bid / out-asked by Shaver.
+
+\begin{figure}[h!] \includegraphics[width=80mm]{SHVR1AA1_180_all_bids.png}
+\caption {1 AA versus 1 Shaver. This plot shows the time the time and price of the bids made.}
+\end{figure}
+
+\begin{figure}[h!] \includegraphics[width=80mm]{SHVR1AA1_180_all_asks.png}
+\caption {1 AA versus 1 Shaver. This plot shows the time the time and price of the asks made.}
+\end{figure}
+
+\subsubsection{1 v Many} In these experiments, trading starts at around round
+90. In the graphs below, we see that the Shaver bots tend towards the
+equilibrium much faster than when there was only one bot; this is likely due to
+there being 10 Shaver bots which are all trying to out-bid each other. When the
+bids and asks converge, the Shaver bots invariably trade with themselves. Our
+AA implementation is excluded from trading as it can't adjust its
+aggressiveness quickly enough. Not all Shaver bots are engaged in making actual
+trades at all times, the horizontal lines of bids / asks on the graphs indicate
+that a Shaver bot is placing shouts at its limit price.
+
+\begin{figure}[h!] \includegraphics[width=80mm]{SHVR10AA1_180_all_bids.png}
+\caption {1 AA versus 10 Shavers. This plot shows the time the time and price of the bids made.}
+\end{figure}
+
+\begin{figure}[h!] \includegraphics[width=80mm]{SHVR10AA1_180_all_asks.png}
+\caption {1 AA versus 10 Shavers. This plot shows the time the time and price of the asks made.}
+\end{figure}
+
+Our AA implmentation again demonstrates how it is not tending to the
+equilibrium logarithmically as it shold be. Were it functioning correctly, our
+AA implementation should have placed bids that were higher (or asks that were
+smaller) just after those Shaver placed. This is because AA is designed to
+alter its aggressiveness such that it can make competitive shouts in subsequent
+rounds, however, it fails to do this. In other words, Adaptive Aggressive is
+failing to change it's aggressiveness adaptively.
+
+\subsubsection{Many v Many} Again, trading begins at around round 90. We see
+the same pattern as we do in the previous experiment except that AA is making
+more bids / asks. On this occasion we see that AA actually manages to make a
+few profitable trades between rounds 90 and 140 before being swamped by the
+simpler and more effective aggressiveness function of the correctly implemented
+Shaver bot. These few trades are more by chance than by design; the dip in bid
+price would have intersected with the poorly adapting AA bot allowing AA to
+place bids that would be accepted by the seller Shaver traders.
 

### 2012-12-03 report/paper.tex
All the paper
Signed-off-by: Sam Phippen <samphippen@googlemail.com>

--- 2012-12-03 report/paper.tex
@@
 
-\subsection{Totally open market}
+\subsubsection{Totally open market}
 
@@
 
+The results of this experiment are fairly clear with 164 trials containing
+non-zero trading and ZIC winning 115 of these with a median profit of 26973.0
+versus a median profit of 0 for our agent the Wilcoxon test shows a clear
+statisitical edge for ZIC (p < 0.01).
+
+\subsubsection{Massive financial crash}
+
+In this test we start with a fairly stable market with the price ranging
+between 600 and 700. We then intentionally very rapidly crash the market by
+dropping the price range to 1-100 for a short range of time before slowly
+ramping the price back up.  Refer to figure 4 for the ask and bid orders
+issued in one of the 300 example runs.
+
+The rationale behind this is the fact that our agent tracks the equilibrium price
+with some accuracy, and as such may be able to more efficiently issue a trade
+than ZIC, which is placing its trades at random within the limit prices it has
+been given.
+
+In these conditions it is of course extremely difficult for any agent to act
+within the market. We have also included a graph of our agent's equilibrium
+estimator, this shows that the estimate does a pretty good job keeping up with
+the extreme turbulence within the market.
+
+In this experiment all 300 trials had cases where trading occurs. Of these 189
+were lost by our agent, however, the medians had a significantly smaller
+difference (ZIC 739.47, our agents 519.072136). Whilst this still represents a
+statistically significant advantage (p < 0.01 Wilcoxon) for ZIC, it raises an
+interesting case where the performance of our agent is significantly improved.
+This lead us to our next experiment, which was to effectively repeatedly crash
+and restore the market, causing an extremely high volatility.
+
+\begin{figure}[h!] \includegraphics[width=80mm]{crash.png} \caption{Market
+order prices given to both buyers and sellers. Extreme volatility introduced at
+t=180 by suddenly crashing the market.} \end{figure}
+
+\begin{figure}[h!]
+\includegraphics[width=80mm]{crash2.png} \caption{Equilibrium estimate of both
+our agent's buyer and seller versions} \end{figure}
+
+\subsubsection{Square wave market}
+
+In this experiment we start with the same inital conditions as the previous
+market but we repeatedly change the price ranges from 600-700 and 1-100 and use
+the "random" stepmode in an attempt to cause maximum market volatility.
+
+The basic rationale of this experiment is that our agent performed better in
+the volatile conditions of the previous experiment, but still performed worse
+than ZIC. We wanted to see if this edge case might cause best case behaviour in
+our agent. In figure 6 we have provided an example of what the orders placed look
+like.
+
+\begin{figure}[h!] \includegraphics[width=80mm]{squarewave.png} \caption{Market
+order prices given to both buyers and sellers. Periodic volatility introduced
+every 180 timesteps} \end{figure}
+
+Unfortunately this experiment did not produce the expected results, with ZIC
+managing to extract a much higher median profit than in the previous experiment
+(1535.48). Our agent also extracted a slightly higher profit than the previous
+experiment (median 703.82).
+
+From these analysis we basically conclude that whilst our bot trades more
+efficiently than giveaway it does not trade more efficiently than ZIC in both
+stable and extremely unstable market conditions. Whilst this is disappointing
+we find an obvious reason for this result: our implementation, which attempts
+to follow the maths in the original Vytelingum\cite{Vytellingum:AA} paper,
+there are flaws in the implementation which cause it not to trade anywhere near
+as efficiently as expected, causing it to essentially fail to trade.
+
+Our implementation also seems to issue significantly fewer trades than would be
+expected
+--luke expand this
+
+\section{Analysing the other traders}
+
+In this section we wanted to analyse the ZIP agent against all the others.
+Based on the COMSM2006\cite{cliff:lecture} lecture about trading agents.
+Specifically the lecture references an article written by D. Cliff which is
+meant to show a case where ZIC traders will not converge to the equilibrium
+price of the market\cite{cliff:minimalint}.
+
 %
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
-\bibliographystyle{abbrv}
-\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
+% The following two commands are all you need in the initial runs of your .tex
+% file to produce the bibliography for the citations in your paper.
+\bibliographystyle{abbrv} \bibliography{paper}  % sigproc.bib is the name of
+the Bibliography in this case
+% You must have a proper ".bib" file and remember to run: latex bibtex latex
+% latex to resolve all references
 %
@@
 %
-%APPENDICES are optional
-%\balancecolumns
-\appendix
-\end{document}
+%APPENDICES are optional \balancecolumns
+\appendix \end{document}

### 2012-12-03 report/sigproc-sp.tex
All the paper
Signed-off-by: Sam Phippen <samphippen@googlemail.com>

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

\documentclass{acm_proc_article-sp}

\begin{document}

\title{A Sample {\ttlit ACM} SIG Proceedings Paper in LaTeX
Format\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Wallamaloo, New Zealand}\\
       \email{trovato@corporation.com}
% 2nd. author
\alignauthor
G.K.M. Tobin\titlenote{The secretary disavows
any knowledge of this author's actions.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
% 3rd. author
\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
one who did all the really hard work.}\\
       \affaddr{The Th{\o}rv{\"a}ld Group}\\
       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
       \affaddr{Hekla, Iceland}\\
       \email{larst@affiliation.org}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Lawrence P. Leipuner\\
       \affaddr{Brookhaven Laboratories}\\
       \affaddr{Brookhaven National Lab}\\
       \affaddr{P.O. Box 5000}\\
       \email{lleipuner@researchlabs.org}
% 5th. author
\alignauthor Sean Fogarty\\
       \affaddr{NASA Ames Research Center}\\
       \affaddr{Moffett Field}\\
       \affaddr{California 94035}\\
       \email{fogartys@amesres.org}
% 6th. author
\alignauthor Charles Palmer\\
       \affaddr{Palmer Research Laboratories}\\
       \affaddr{8600 Datapoint Drive}\\
       \affaddr{San Antonio, Texas 78229}\\
       \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms to
the formatting guidelines for ACM SIG Proceedings.
It complements the document \textit{Author's Guide to Preparing
ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file.
\end{abstract}

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Theory}

\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings

\section{Introduction}
The \textit{proceedings} are the records of a conference.
ACM seeks to give these conference by-products a uniform,
high-quality appearance.  To do this, ACM has some rigid
requirements for the format of the proceedings documents: there
is a specified format (balanced  double columns), a specified
set of fonts (Arial or Helvetica and Times Roman) in
certain specified sizes (for instance, 9 point for body copy),
a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
and (1.9 cm [.75"]) left and right; specified column width
(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).

The good news is, with only a handful of manual
settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
and {\texttt{\char'134 alignauthor}} commands, you have
already used; another, {\texttt{\char'134 balancecolumns}}, will
be used in your very last run of \LaTeX\ to ensure
balanced column heights on the last page.}, the \LaTeX\ document
class file handles all of this for you.

The remainder of this document is concerned with showing, in
the context of an ``actual'' document, the \LaTeX\ commands
specifically available for denoting the structure of a
proceedings paper, rather than with giving rigorous descriptions
or explanations of such commands.

\section{The {\secit Body} of The Paper}
Typically, the body of a paper is organized
into a hierarchical structure, with numbered or unnumbered
headings for sections, subsections, sub-subsections, and even
smaller sections.  The command \texttt{{\char'134}section} that
precedes this paragraph is part of such a
hierarchy.\footnote{This is the second footnote.  It
starts a series of three footnotes that add nothing
informational, but just give an idea of how footnotes work
and look. It is a wordy one, just so you see
how a longish one plays out.} \LaTeX\ handles the numbering
and placement of these headings for you, when you use
the appropriate heading commands around the titles
of the headings.  If you want a sub-subsection or
smaller part to be unnumbered in your output, simply append an
asterisk to the command name.  Examples of both
numbered and unnumbered headings will appear throughout the
balance of this sample document.

Because the entire article is contained in
the \textbf{document} environment, you can indicate the
start of a new paragraph with a blank line in your
input file; that is why this sentence forms a separate paragraph.

\subsection{Type Changes and {\subsecit Special} Characters}
We have already seen several typeface changes in this sample.  You
can indicate italicized words or phrases in your text with
the command \texttt{{\char'134}textit}; emboldening with the
command \texttt{{\char'134}textbf}
and typewriter-style (for instance, for computer code) with
\texttt{{\char'134}texttt}.  But remember, you do not
have to indicate typestyle changes when such changes are
part of the \textit{structural} elements of your
article; for instance, the heading of this subsection will
be in a sans serif\footnote{A third footnote, here.
Let's make this a rather short one to
see how it looks.} typeface, but that is handled by the
document class file. Take care with the use
of\footnote{A fourth, and last, footnote.}
the curly braces in typeface changes; they mark
the beginning and end of
the text that is to be in the different typeface.

You can use whatever symbols, accented characters, or
non-English characters you need anywhere in your document;
you can find a complete list of what is
available in the \textit{\LaTeX\
User's Guide}\cite{Lamport:LaTeX}.

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\subsubsection{Inline (In-text) Equations}
A formula that appears in the running text is called an
inline or in-text formula.  It is produced by the
\textbf{math} environment, which can be
invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
construction or with the short form \texttt{\$. . .\$}. You
can use any of the symbols and structures,
from $\alpha$ to $\omega$, available in
\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
few examples of in-text equations in context. Notice how
this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsubsection{Display Equations}
A numbered display equation -- one set off by vertical space
from the text and centered horizontally -- is produced
by the \textbf{equation} environment. An unnumbered display
equation is produced by the \textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols
and structures available in \LaTeX; this section will just
give a couple of examples of display equations in context.
First, consider the equation, shown as an inline equation above:
\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
and follow it with another numbered equation:
\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\subsection{Citations}
Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
conference
proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
in the Bibliography section of your
article will occur throughout the text of your article.
You should use BibTeX to automatically produce this bibliography;
you simply need to insert one of several citation commands with
a key of the item cited in the proper location in
the \texttt{.tex} file \cite{Lamport:LaTeX}.
The key is a short reference you invent to uniquely
identify each work; in this sample document, the key is
the first author's surname and a
word from the title.  This identifying key is included
with each item in the \texttt{.bib} file for your article.

The details of the construction of the \texttt{.bib} file
are beyond the scope of this sample document, but more
information can be found in the \textit{Author's Guide},
and exhaustive details in the \textit{\LaTeX\ User's
Guide}\cite{Lamport:LaTeX}.

This article shows only the plainest form
of the citation command, using \texttt{{\char'134}cite}.
This is what is stipulated in the SIGS style specifications.
No other citation format is endorsed.

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
is found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table 1 is included in the input file; compare the
placement of the table here with the table in the printed
dvi output of this document.

\begin{table}
\centering
\caption{Frequency of Special Characters}
\begin{tabular}{|c|c|l|} \hline
Non-English or Math&Frequency&Comments\\ \hline
\O & 1 in 1,000& For Swedish names\\ \hline
$\pi$ & 1 in 5& Common in math\\ \hline
\$ & 4 in 5 & Used in business\\ \hline
$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
\hline\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of
the page's live area, use the environment
\textbf{table*} to enclose the table's contents and
the table caption.  As with a single-column table, this wide
table will ``float" to a location deemed more desirable.
Immediately following this sentence is the point at which
Table 2 is included in the input file; again, it is
instructive to compare the placement of the
table here with the table in the printed dvi
output of this document.

\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\subsection{Figures}
Like tables, figures cannot be split across pages; the
best placement for them
is typically the top or the bottom of the page nearest
their initial cite.  To ensure this proper ``floating'' placement
of figures, use the environment
\textbf{figure} to enclose the figure and its caption.

This sample document contains examples of \textbf{.eps}
and \textbf{.ps} files to be displayable with \LaTeX.  More
details on each of these is found in the \textit{Author's Guide}.

As was the case with tables, you may want a figure
that spans two columns.  To do this, and still to
ensure proper ``floating'' placement of tables, use the environment
\textbf{figure*} to enclose the figure and its caption.

Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
used; use
the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
commands as appropriate for the different file types.

\subsection{Theorem-like Constructs}
Other common constructs that may occur in your article are
the forms for logical constructs like theorems, axioms,
corollaries and proofs.  There are
two forms, one produced by the
command \texttt{{\char'134}newtheorem} and the
other by the command \texttt{{\char'134}newdef}; perhaps
the clearest and easiest way to distinguish them is
to compare the two in the output of this sample document:

This uses the \textbf{theorem} environment, created by
the\linebreak\texttt{{\char'134}newtheorem} command:
\newtheorem{theorem}{Theorem}
\begin{theorem}
Let $f$ be continuous on $[a,b]$.  If $G$ is
an antiderivative for $f$ on $[a,b]$, then
\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
\end{theorem}

The other uses the \textbf{definition} environment, created
by the \texttt{{\char'134}newdef} command:
\newdef{definition}{Definition}
\begin{definition}
If $z$ is irrational, then by $e^z$ we mean the
unique number which has
logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
\end{definition}

Two lists of constructs that use one of these
forms is given in the
\textit{Author's  Guidelines}.

and don't forget to end the environment with
{figure*}, not {figure}!

There is one other similar construct environment, which is
already set up
for you; i.e. you must \textit{not} use
a \texttt{{\char'134}newdef} command to
create it: the \textbf{proof} environment.  Here
is a example of its use:
\begin{proof}
Suppose on the contrary there exists a real number $L$ such that
\begin{displaymath}
\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
\end{displaymath}
Then
\begin{displaymath}
l=\lim_{x\rightarrow c} f(x)
= \lim_{x\rightarrow c}
\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
\frac{f(x)}{g(x)} = 0\cdot L = 0,
\end{displaymath}
which contradicts our assumption that $l\neq 0$.
\end{proof}

Complete rules about using these environments and using the
two different creation commands are in the
\textit{Author's Guide}; please consult it for more
detailed instructions.  If you need to use another construct,
not listed therein, which you want to have the same
formatting as the Theorem
or the Definition\cite{salas:calculus} shown above,
use the \texttt{{\char'134}newtheorem} or the
\texttt{{\char'134}newdef} command,
respectively, to create it.

\subsection*{A {\secit Caveat} for the \TeX\ Expert}
Because you have just been given permission to
use the \texttt{{\char'134}newdef} command to create a
new form, you might think you can
use \TeX's \texttt{{\char'134}def} to create a
new command: \textit{Please refrain from doing this!}
Remember that your \LaTeX\ source code is primarily intended
to create camera-ready copy, but may be converted
to other forms -- e.g. HTML. If you inadvertently omit
some or all of the \texttt{{\char'134}def}s recompilation will
be, to say the least, problematic.

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for
the body of the article are different in the appendices.
In the \textbf{appendix} environment, the command
\textbf{section} is used to
indicate the start of each Appendix, with alphabetic order
designation (i.e. the first is A, the second B, etc.) and
a title (if you include one).  So, if you need
hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this
document in Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{Acknowledgments}
\subsection{Additional Authors}
This section is inserted by \LaTeX; you do not insert it.
You just add the names and information in the
\texttt{{\char'134}additionalauthors} command at the start
of the document.
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}
The acm\_proc\_article-sp document class file itself is chock-full of succinct
and helpful comments.  If you consider yourself a moderately
experienced to expert user of \LaTeX, you may find reading
it useful but please remember not to change it.
\balancecolumns
% That's all folks!
\end{document}

### 2012-12-03 report/paper.tex
Added figures to latex.
Referenced figures

@@
 
-\subsubsection{1 v 1} No trading occurs in this experiment. In the graphs
-below, you can see the shouts made by the bots. The Shaver buyer and seller
-traders tend toward the equilibrium price over time but don't manage to reach
-it before the market session ends. The AA bot makes very few trades and is
-always out-bid / out-asked by Shaver.
+\subsubsection{1 v. 1} No trading occurs in this experiment. In figures 2 and 3,
+you can see the shouts made by the bots. The Shaver buyer and seller traders
+tend toward the equilibrium price over time but don't manage to reach it before
+the market session ends. The AA bot makes very few trades and is always out-bid
+/ out-asked by Shaver.
 
 \begin{figure}[h!] \includegraphics[width=80mm]{SHVR1AA1_180_all_bids.png}
-\caption {1 AA versus 1 Shaver. This plot shows the time the time and price of the bids made.}
+\caption {1 AA versus 1 Shaver}
 \end{figure}
@@
 \begin{figure}[h!] \includegraphics[width=80mm]{SHVR1AA1_180_all_asks.png}
-\caption {1 AA versus 1 Shaver. This plot shows the time the time and price of the asks made.}
+\caption {1 AA versus 1 Shaver}
 \end{figure}
 
-\subsubsection{1 v Many} In these experiments, trading starts at around round
-90. In the graphs below, we see that the Shaver bots tend towards the
+\subsubsection{1 v. Many} In these experiments, trading starts at around round
+90. In figures 4 and 5, we see that the Shaver bots tend towards the
 equilibrium much faster than when there was only one bot; this is likely due to
@@
 \begin{figure}[h!] \includegraphics[width=80mm]{SHVR10AA1_180_all_bids.png}
-\caption {1 AA versus 10 Shavers. This plot shows the time the time and price of the bids made.}
+\caption {1 AA versus 10 Shavers}
 \end{figure}
@@
 \begin{figure}[h!] \includegraphics[width=80mm]{SHVR10AA1_180_all_asks.png}
-\caption {1 AA versus 10 Shavers. This plot shows the time the time and price of the asks made.}
+\caption {1 AA versus 10 Shavers}
 \end{figure}
@@
 
-\subsubsection{Many v Many} Again, trading begins at around round 90. We see
-the same pattern as we do in the previous experiment except that AA is making
-more bids / asks. On this occasion we see that AA actually manages to make a
-few profitable trades between rounds 90 and 140 before being swamped by the
-simpler and more effective aggressiveness function of the correctly implemented
-Shaver bot. These few trades are more by chance than by design; the dip in bid
-price would have intersected with the poorly adapting AA bot allowing AA to
-place bids that would be accepted by the seller Shaver traders.
+\subsubsection{Many v Many} Again, trading begins at around round 90. In figures
+6 and 7, we see the same pattern as we do in the previous experiment except that
+AA is making more bids / asks. On this occasion we see that AA actually manages
+to make a few profitable trades between rounds 90 and 140 before being swamped
+by the simpler and more effective aggressiveness function of the correctly
+implemented Shaver bot. These few trades are more by chance than by design; the
+dip in bid price would have intersected with the poorly adapting AA bot allowing
+AA to place bids that would be accepted by the seller Shaver traders.
+
+\begin{figure}[h!] \includegraphics[width=80mm]{SHVR10AA10_180_all_bids.png}
+\caption {10 AAs versus 10 Shavers}
+\end{figure}
+
+\begin{figure}[h!] \includegraphics[width=80mm]{SHVR10AA10_180_all_asks.png}
+\caption {10 AAs versus 10 Shavers}
+\end{figure}
 

### 2012-12-03 BSE.py
Changed graph code slightly.

@@ -1056,9 +1056,11 @@ def market_session(sess_id, starttime, endtime, trader_spec, order_schedule, dum
 
         make_pretty_graph(orders_returned, traders_spec["buyers"], endtime)
 
+        '''
         for t in traders:
             if traders[t].ttype == "AA":
                 traders[t].graph_values(traders_spec["buyers"], endtime)
+        '''
 
 #############################
 
@@ -1078,21 +1080,28 @@ def make_pretty_graph(orders_returned, spec, length):
         prices = [x.price for x in type_orders]
         plt.figure(3)
         if t == "AA":
-            plt.plot(times, prices, 'ro')
+            plt.plot(times, prices, 'ro', label=t)
         else:
-            plt.plot(times, prices, 'rx')
+            plt.plot(times, prices, 'rx', label=t)
+        plt.legend(loc = 2)
+        plt.ylabel("Price")
+        plt.xlabel("Time")
+            
         type_orders = [x[1] for x in asks if x[0] == t]
         times = [x.time for x in type_orders]
         prices = [x.price for x in type_orders]
         plt.figure(4)
         if t == "AA":
-            plt.plot(times, prices, 'bo')
+            plt.plot(times, prices, 'bo', label=t)
         else:
-            plt.plot(times, prices, 'bx')
+            plt.plot(times, prices, 'bx', label=t)
+        plt.legend(loc = 3)
+        plt.ylabel("Price")
+        plt.xlabel("Time")
     plt.figure(3)
-    plt.savefig("figures/" + spec_str + "_" + length + "_all_bids.png")
+    plt.savefig("figures/" + spec_str + "_" + str(int(length)) + "_all_bids.png")
     plt.figure(4)
-    plt.savefig("figures/" + spec_str + "_" + length + "_all_asks.png")
+    plt.savefig("figures/" + spec_str + "_" + str(int(length)) + "_all_asks.png")
     
 
 ## Below here is where we set up and run a series of experiments
@@ -1116,7 +1125,7 @@ if __name__ == "__main__":
         order_sched = {'sup':supply_schedule, 'dem':demand_schedule,
                        'interval':30, 'timemode':'drip-poisson'}
 
-        buyers_spec = [('SHVR',1),('AA',1)]
+        buyers_spec = [('SHVR',10),('AA',10)]
         sellers_spec = buyers_spec
         traders_spec = {'sellers':sellers_spec, 'buyers':buyers_spec}
 

### 2012-12-03 report/paper.tex
Added less bidding explanation.

@@
 tend toward the equilibrium price over time but don't manage to reach it before
-the market session ends. The AA bot makes very few trades and is always out-bid
+the market session ends. The AA bot makes very few shouts and is always out-bid
 / out-asked by Shaver.
@@
 
-\subsubsection{1 v. Many} In these experiments, trading starts at around round
+\subsubsection{1 v. Many} With more Shaver bots, trading starts at around round
 90. In figures 4 and 5, we see that the Shaver bots tend towards the
-equilibrium much faster than when there was only one bot; this is likely due to
-there being 10 Shaver bots which are all trying to out-bid each other. When the
-bids and asks converge, the Shaver bots invariably trade with themselves. Our
-AA implementation is excluded from trading as it can't adjust its
-aggressiveness quickly enough. Not all Shaver bots are engaged in making actual
-trades at all times, the horizontal lines of bids / asks on the graphs indicate
-that a Shaver bot is placing shouts at its limit price.
+equilibrium as before but at a much faster rate than when there was only one
+bot; this is likely due to there being 10 Shaver bots which are all trying to
+out-bid each other. When the bids and asks converge, the Shaver bots invariably
+trade with themselves. Our AA implementation is excluded from trading as it
+can't adjust its aggressiveness quickly enough. Not all Shaver bots are engaged
+in making actual trades at all times, the horizontal lines of bids / asks on the
+graphs indicate that a Shaver bot is placing shouts at its limit price.
 
@@
 Our implementation also seems to issue significantly fewer trades than would be
-expected
---luke expand this
+expected. Looking at the implemeentations of the other bots provided by D.
+Cliff, it is not hard to see why. The implementations provided will always
+return a trade when the bot has an order to fulfil (with the exception of the
+Sniper bot which will make a shout on every round after a give threshold)
+meaning these implementations have many more shouts on which to make profit.
+
+This is contrary to our AA implementation which will not return a trade in the
+case where the best bid in the market is greater than (for a buyer), or where
+the best ask is less than (for a seller), the bot's limit price. This results
+in our AA implementation not sharing it's information with the market which
+would prevent other bots making offers that are more favourable to our AA bot.
+
+\begin{enumerate}
+\item
 

### 2012-12-03 report/paper.tex
Fix some things
Signed-off-by: Sam Phippen <samphippen@googlemail.com>

--- 2012-12-03 report/paper.tex
@@
 \documentclass{acm_proc_article-sp}
+\usepackage{url}
 
@@
 
+\begin{figure}[h!] \includegraphics[width=80mm]{SHVR10AA10_180_all_bids.png}
+\caption {10 AAs versus 10 Shavers. This plot shows the time the time and price of the bids made.}
+\end{figure}
+
+\begin{figure}[h!] \includegraphics[width=80mm]{SHVR10AA10_180_all_asks.png}
+\caption {10 AAs versus 10 Shavers. This plot shows the time the time and price of the asks made.}
+\end{figure}
+
 \subsection{1 v 1 tests} Given these initially dismal results, we decided that
@@
 were won by our agent. The distributions of profit for each agent, as well as
-the distribution of differences in profit can be seen in figures 2 and 3.
+the distribution of differences in profit can be seen in figures 8 and 9.
 
@@
 In light of the test against Giveaway it is  worth noting the spike at a profit
-of around ~4000 in figure 3.  These occasions correspond to Giveaway making
+of around ~4000 in figure 9.  These occasions correspond to Giveaway making
 4000 more profit than our agent. A quick analysis of the data indicates that
@@
 dropping the price range to 1-100 for a short range of time before slowly
-ramping the price back up.  Refer to figure 4 for the ask and bid orders
+ramping the price back up.  Refer to figure 10 for the ask and bid orders
 issued in one of the 300 example runs.
@@
 than ZIC. We wanted to see if this edge case might cause best case behaviour in
-our agent. In figure 6 we have provided an example of what the orders placed look
-like.
+our agent. In figure 12 we have provided an example of what the orders placed
+look like.
 
@@
 % file to produce the bibliography for the citations in your paper.
-\bibliographystyle{abbrv} \bibliography{paper}  % sigproc.bib is the name of
-the Bibliography in this case
+\bibliographystyle{acm} \bibliography{paper}  % sigproc.bib is the name of
 % You must have a proper ".bib" file and remember to run: latex bibtex latex

### 2012-12-04 report/paper.tex
Fix the paper
Signed-off-by: Sam Phippen <samphippen@googlemail.com>
Paper update.
Signed-off-by: Sam Phippen <samphippen@googlemail.com>

@@
 \end{figure}
+
+Luke can you make this connect better
 
@@
 Our implementation also seems to issue significantly fewer trades than would be
-expected. Looking at the implemeentations of the other bots provided by D.
+expected. Looking at the implementations of the other bots provided by D.
 Cliff, it is not hard to see why. The implementations provided will always
@@
 
-\begin{enumerate}
-\item
+\section{ZIC versus ZIP in the square wave market}
 
-\section{Analysing the other traders}
+Contrary to our initial intuitions, the previously described square wave market
+conditions caused an interesting behaviour when comparing ZIP and ZIC in a one
+versus one fashion. ZIC actually beat ZIP 65 out of 100 times when running this
+test. The median profit for ZIC agents was 1793.5, beating ZIP's median profit
+of 1487.25. Using the Wilcoxon test showed that this difference of medians was
+statistically significant (p < 0.01).
 
-In this section we wanted to analyse the ZIP agent against all the others.
-Based on the COMSM2006\cite{cliff:lecture} lecture about trading agents.
-Specifically the lecture references an article written by D. Cliff which is
-meant to show a case where ZIC traders will not converge to the equilibrium
-price of the market\cite{cliff:minimalint}.
+In figure n we show the trades issued by each agent in one of our sample runs
+with time within the trading session, along with the agent's limit price when
+the trade was created.
+
+--luke can you fill this out explaining why this happened
+
+Even in this admittedly artificial environment it is interesting to note that
+whilst in realistic environments the more advanced traders may dominate, in
+obscenely volatile markets, this result may indicate that less intelligent
+traders that do not introspect the market may be better at generating profit.
+
+\section{Conclusions}
+
+Whilst we attempted to implement the adaptive aggressive algorithm, it is
+pretty clear based on the analysis presented in this paper that our
+implementation falls short. Whilst it is able to trade more efficiently than
+the Giveaway trader in one versus one cases, with a simple supply and demand
+schedule, the results from the rest of the analysis presented indicate that our
+agent would not be the one to use if one were desperately motivated to make
+incredible profits.
+
+We also analysed the case that produces worst case behaviour in our agent,
+which is when it is placed against a shaver trading agent in a many versus many
+fashion. In this case our agent is found to generate a small loss. This occurs
+because of shaver's rapid descent to the mean (luke can you check this).
+
+Finally we produced an analysis showing that in a very volatile market, the
+less "intelligent" ZIP agent is able to generate more profit than the ZIC
+agent. We posit this is because the trend analysis that ZIP attempts to make
+cannot be accurate, due to the rapidly oscillating nature of the market.
 

### 2012-12-05 report/paper.tex
Beat some things.
Signed-off-by: Sam Phippen <samphippen@googlemail.com>

@@
 
-Luke can you make this connect better
-
-\subsection{AA v Shaver} One very noticable trend in our analysis is when AA
-is pitched against the Shaver algorithm. In all of our experiments where trades
-occurred, Shaver made more profit than AA. In this section, we explore the
-reasons why Shaver so completely outclasses our implemetation of AA.
+\subsection{AA v Shaver} In the previous section, our AA implementation is
+pitched against the Shaver algorithm. In these experiments, Shaver made more
+profit than AA. In this section, we explore the reasons why Shaver so
+completely outclasses our implementation of AA, causing it to make a loss in a
+number of experiments.
 
@@
 the best bid on the market. This is similar to how AA's aggressiveness is
-supposed to operate; when a bid is placed that out-bids the bot, the price is
-adjusted so that the bot out-bids the previous bid in the following round
-(unless such a bid would exceed the bot's limit price). This aggressiveness
+supposed to operate; when a bid is placed that out-bids the agent, the price is
+adjusted so that the agent out-bids the previous bid in the following round
+(unless such a bid would exceed the agent's limit price). This aggressiveness
 behaviour increases the chance of a trade and thus increases profit.
@@
 \begin{enumerate}
-\item 1 AA bot v. 1 Shaver bot
-\item 1 AA bot v. 10 Shaver bots
-\item 10 AA bots v. 10 Shaver bots
+\item 1 AA agent v. 1 Shaver agent
+\item 1 AA agent v. 10 Shaver agents
+\item 10 AA agents v. 10 Shaver agents
 \end{enumerate}
@@
 \subsubsection{1 v. 1} No trading occurs in this experiment. In figures 2 and 3,
-you can see the shouts made by the bots. The Shaver buyer and seller traders
+you can see the shouts made by the agents. The Shaver buyer and seller traders
 tend toward the equilibrium price over time but don't manage to reach it before
-the market session ends. The AA bot makes very few shouts and is always out-bid
+the market session ends. The AA agent makes very few shouts and is always out-bid
 / out-asked by Shaver.
@@
 
-\subsubsection{1 v. Many} With more Shaver bots, trading starts at around round
-90. In figures 4 and 5, we see that the Shaver bots tend towards the
+\subsubsection{1 v. Many} With more Shaver agents, trading starts at around round
+90. In figures 4 and 5, we see that the Shaver agents tend towards the
 equilibrium as before but at a much faster rate than when there was only one
-bot; this is likely due to there being 10 Shaver bots which are all trying to
-out-bid each other. When the bids and asks converge, the Shaver bots invariably
+agent; this is likely due to there being 10 Shaver agents which are all trying to
+out-bid each other. When the bids and asks converge, the Shaver agents invariably
 trade with themselves. Our AA implementation is excluded from trading as it
-can't adjust its aggressiveness quickly enough. Not all Shaver bots are engaged
+can't adjust its aggressiveness quickly enough. Not all Shaver agents are engaged
 in making actual trades at all times, the horizontal lines of bids / asks on the
-graphs indicate that a Shaver bot is placing shouts at its limit price.
+graphs indicate that a Shaver agents is placing shouts at its limit price.
 
@@
 by the simpler and more effective aggressiveness function of the correctly
-implemented Shaver bot. These few trades are more by chance than by design; the
-dip in bid price would have intersected with the poorly adapting AA bot allowing
+implemented Shaver agents. These few trades are more by chance than by design; the
+dip in bid price would have intersected with the poorly adapting AA agents allowing
 AA to place bids that would be accepted by the seller Shaver traders.
+
+--conclusion paragraph here plz luke
 
@@
 300 1v1 tests were performed, we used the same schedule as the many versus many
-test, with a longer total trading time of 1800. Results where both bots made
+test, with a longer total trading time of 1800. Results where both agents made
 zero profit were eliminated, this brought the number of tests included for
@@
 \caption{Histogram of profit distributions over 300 similar trading runs for
-the two bot types used in the 1v1 test. Note axis are different for the two
-bots} \end{figure}
+the two agents types used in the 1v1 test. Note axis are different for the two
+agents} \end{figure}
 
@@
 
-From these analysis we basically conclude that whilst our bot trades more
+From these analysis we basically conclude that whilst our agents trades more
 efficiently than giveaway it does not trade more efficiently than ZIC in both
@@
 Our implementation also seems to issue significantly fewer trades than would be
-expected. Looking at the implementations of the other bots provided by D.
+expected. Looking at the implementations of the other agents provided by D.
 Cliff, it is not hard to see why. The implementations provided will always
-return a trade when the bot has an order to fulfil (with the exception of the
-Sniper bot which will make a shout on every round after a give threshold)
+return a trade when the agent has an order to fulfil (with the exception of the
+Sniper agent which will make a shout on every round after a give threshold)
 meaning these implementations have many more shouts on which to make profit.
@@
 case where the best bid in the market is greater than (for a buyer), or where
-the best ask is less than (for a seller), the bot's limit price. This results
+the best ask is less than (for a seller), the agent's limit price. This results
 in our AA implementation not sharing it's information with the market which
-would prevent other bots making offers that are more favourable to our AA bot.
-
+would prevent other agents making offers that are more favourable to our AA agent.
+\newpage
 \section{ZIC versus ZIP in the square wave market}
@@
 
-In figure n we show the trades issued by each agent in one of our sample runs
+In figure 13 we show the trades issued by each agent in one of our sample runs
 with time within the trading session, along with the agent's limit price when
@@
 
---luke can you fill this out explaining why this happened
+\begin{figure} \includegraphics[width=80mm]{omg_zip_zic.png}
+\caption{Example of bids and asks issued by ZIC and ZIP in a market with the
+conditions of this experiment}
+\end{figure}
+
+Figure 13 clearly shows why ZIC is able to outperform ZIP in this market. As the
+market price rapidly shifts ZIC simply redistributes it's prices randomly
+throughout the possible range of prices, ZIP's internal profit margin changes
+in response to what everyone else is doing. However as the market is peturbing
+randomly, and the ZIC agents are trading randomly, this estimate is likely to
+be wildly thrown off. The reason ZIC can trade is that it's offers will always
+eventually "meet in the middle", regardless of the, massive, random variation.
 
